---
title: "Exercise 1"
author: "Rafael S. Müller"
date: "15 9 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
library(ggplot2)
```
# Log-Normal Distribution

First, we set the parameters for the log normal distribution.

```{r}
v_mean <- 1
v_sd <- 0.25
n <- 100
```

We take `r n` samples from a log-normal distribution with a mean of `r v_mean` and a standard deviation of `r v_sd`.

```{r cars}
df <- data.frame(smp=stats::rlnorm(n, meanlog = v_mean, sdlog = v_sd))
```

## Histogram (standard scale)
First, we look at a histogram with standard scale.

```{r}

ggplot2::ggplot(df, aes(x=smp)) +
  ggplot2::geom_histogram(bins=8, color="black", fill="white") +
  ggplot2::xlab("log-normal dist")
```

## Histogram (log scale)
Next, we plot the histogram with log scale.

```{r}
ggplot2::ggplot(df, aes(x=log(smp))) +
  ggplot2::geom_histogram(bins = 8, color="black", fill="white") +
  ggplot2::xlab("log-normal dist")
```

## Summary

The mean and standard deviation of the sampled log-normal distribution are `r base::round(base::mean(df$smp), digits = 2)` and `r base::round(stats::sd(df$smp), digits = 2) `,respectively

